---
title: "Saskatoon W2 Test Data Code"
author: "Daniel Fuller"
date: '2023-06-19'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(purrr)
library(readr)
library(archive)
library(devtools)
library(inborutils)
library(dbplyr)
```

# Creating directory structure

Creating directory structure for interact test data

```{}
cd Documents
mkdir interact_test_data
cd interact_test_data

##### Saskatoon Folders

mkdir saskatoon montreal victoria vancouver
cd saskatoon
ls 
mkdir wave_01 wave_02 wave_03 wave_04

mkdir wave_01/ethica wave_01/sensedoc wave_02/ethica wave_02/sensedoc wave_03/ethica wave_03/sensedoc wave_04/ethica wave_04/sensedoc

##### Montreal Folders

cd ~/Documents/interact_test_data/montreal
ls 
mkdir wave_01 wave_02 wave_03 wave_04

mkdir wave_01/ethica wave_01/sensedoc wave_02/ethica wave_02/sensedoc wave_03/ethica wave_03/sensedoc wave_04/ethica wave_04/sensedoc

##### Vancouver Folders

cd ~/Documents/interact_test_data/vancouver
ls 
mkdir wave_01 wave_02 wave_03 wave_04

mkdir wave_01/ethica wave_01/sensedoc wave_02/ethica wave_02/sensedoc wave_03/ethica wave_03/sensedoc wave_04/ethica wave_04/sensedoc


##### Victoria Folders

cd ~/Documents/interact_test_data/victoria
ls 
mkdir wave_01 wave_02 wave_03 wave_04

mkdir wave_01/ethica wave_01/sensedoc wave_02/ethica wave_02/sensedoc wave_03/ethica wave_03/sensedoc wave_04/ethica wave_04/sensedoc
```

# Data prep for Saskatoon

# Wave 2 Saskatoon

## Linkage files

```{r}
setwd("/Volumes/extender/all_data/")

linkage_sk_w2 <- read_csv("/Volumes/extender/interact_test_data/saskatoon/wave_02/linkage.csv")

linkage_sk_w2 <- arrange(linkage_sk_w2, ethica_id)
linkage_sk_w2 <- slice(linkage_sk_w2, 1:6)

write_csv(linkage_sk_w2, "/Volumes/extender/interact_test_data/saskatoon/wave_02/linkage_wave_02_saskatoon.csv")

linkage_wave_02_saskatoon <- linkage_sk_w2$interact_id

ethica_wave_02_saskatoon <- linkage_sk_w2$ethica_id
```

## Sensedoc 

Creating folders for each participant that exists in the linkage file

```{}
base_path <- "/Users/dlf545/Documents/interact_test_data/saskatoon/wave_02/sensedoc"

for (name in linkage_wave_02_saskatoon) {

 path <- paste0(base_path, "/", name)
 dir.create(path)

}
```

Sensedoc data has format `interact_id_sensedoc_serial` these are columns that are available in the linkage file. In principle we only to link on `interact_id` but it's possible that a person has two sensedocs because one broke during their participation time. Also, because sensedoc as used with multiple participants there are many cases where sensedocs serial is repeated. 

Because this is test data I'm just going to manually move the `.SDB` files to the correct folders. This will probably not be the case in real life... but that's not my problem. 

OK done. 

## Ethica Data Prep

```{}
base_path <- "/Users/dlf545/Documents/interact_test_data/saskatoon/wave_02/ethica"

for (name in linkage_wave_02_saskatoon) {

 path <- paste0(base_path, "/", name)
 dir.create(path)

}
```

Reading in a writing ethica data to specific participant folders

```{r}
### Testing with battery data
read_csv(archive_read("/Volumes/extender/all_data/all_studies_battery.tar.gz", file = "2341_battery.csv")) %>%
            filter(., user_id == ethica_wave_02_saskatoon) %>%
            group_split(user_id) %>%
            iwalk(~ write_csv(.x, str_c('battery_wave_02', .y, '_ethica.csv')))
```

```{r}
### GPS Data
read_csv(archive_read("/Volumes/extender/all_data/all_studies_gps.tar.gz", file = "2341_gps.csv")) %>%
            filter(., user_id == ethica_wave_02_saskatoon) %>%
            group_split(user_id) %>%
            iwalk(~ write_csv(.x, str_c('gps_wave_02', .y, '_ethica.csv')))
gc()
```

```{r}
### Bluetooth Data
read_csv(archive_read("/Volumes/extender/all_data/all_studies_bluetooth.tar.gz", file = "2341_bluetooth.csv")) %>%
            filter(., user_id == ethica_wave_02_saskatoon) %>%
            group_split(user_id) %>%
            iwalk(~ write_csv(.x, str_c('bluetooth_wave_02', .y, '_ethica.csv')))
gc()
```

No Bluetooth data

```{r}
### Mbar Data
read_csv(archive_read("/Volumes/extender/all_data/all_studies_mbar.tar.gz", file = "2341_mb_activity_rec.csv")) %>%
            filter(., user_id == ethica_wave_02_saskatoon) %>%
            group_split(user_id) %>%
            iwalk(~ write_csv(.x, str_c('mbar_wave_02', .y, '_ethica.csv')))
gc()
```

```{r}
### Pedometer Data
read_csv(archive_read("/Volumes/extender/all_data/all_studies_pedometer.tar.gz", file = "2341_pedometer.csv")) %>%
            filter(., user_id == ethica_wave_02_saskatoon) %>%
            group_split(user_id) %>%
            iwalk(~ write_csv(.x, str_c('pedometer_wave_02', .y, '_ethica.csv')))
gc()
```

## Accel Data

```{r}
sqlite_file_w2_sk <- "ethica_wave_02_saskatoon"
table_file_w2_sk <- "accel_e_wave_02_saskatoon"

inborutils::csv_to_sqlite(csv_file = "/Volumes/extender/all_data/2341_accelerometer.csv", 
              sqlite_file_w2_sk, table_file_w2_sk, pre_process_size = 1000, 
              chunk_size = 50000, show_progress_bar = TRUE)

con <- DBI::dbConnect(SQLite(), dbname = "ethica_wave_02_saskatoon")
accel_w2_ethica_sk <- tbl(con, "accel_e_wave_02_saskatoon")
accel_w2_ethica_sk

### Participant 5410

accel_wave_02_ethica_5410 <- accel_w2_ethica_sk %>% 
                                      filter(user_id == 5410) 
accel_wave_02_ethica_5410 <- accel_wave_02_ethica_5410 %>% collect()

write_csv(accel_wave_02_ethica_5410, "accel_wave_02_ethica_5410.csv")
rm(accel_wave_02_ethica_5410)

### Participant 1030

accel_wave_01_ethica_1030 <- accel_w1_ethica_sk %>% 
                                      filter(user_id == 1030) 
accel_wave_01_ethica_1030 <- accel_wave_01_ethica_1030 %>% collect()

write_csv(accel_wave_01_ethica_1030, "accel_wave_02_ethica_1030.csv")
rm(accel_wave_01_ethica_1030)
```
