---
title: "Saskatoon W1 Test Data Code"
author: "Daniel Fuller"
date: '2023-06-19'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(purrr)
library(readr)
library(archive)
library(devtools)
library(inborutils)
library(dbplyr)
```

# Creating directory structure

Creating directory structure for interact test data

```{}
cd Documents
mkdir interact_test_data
cd interact_test_data

##### Saskatoon Folders

mkdir saskatoon montreal victoria vancouver
cd saskatoon
ls 
mkdir wave_01 wave_02 wave_03 wave_04

mkdir wave_01/ethica wave_01/sensedoc wave_02/ethica wave_02/sensedoc wave_03/ethica wave_03/sensedoc wave_04/ethica wave_04/sensedoc

##### Montreal Folders

cd ~/Documents/interact_test_data/montreal
ls 
mkdir wave_01 wave_02 wave_03 wave_04

mkdir wave_01/ethica wave_01/sensedoc wave_02/ethica wave_02/sensedoc wave_03/ethica wave_03/sensedoc wave_04/ethica wave_04/sensedoc

##### Vancouver Folders

cd ~/Documents/interact_test_data/vancouver
ls 
mkdir wave_01 wave_02 wave_03 wave_04

mkdir wave_01/ethica wave_01/sensedoc wave_02/ethica wave_02/sensedoc wave_03/ethica wave_03/sensedoc wave_04/ethica wave_04/sensedoc


##### Victoria Folders

cd ~/Documents/interact_test_data/victoria
ls 
mkdir wave_01 wave_02 wave_03 wave_04

mkdir wave_01/ethica wave_01/sensedoc wave_02/ethica wave_02/sensedoc wave_03/ethica wave_03/sensedoc wave_04/ethica wave_04/sensedoc
```

# Data prep for Saskatoon

# Wave 1 Saskatoon

## Linkage files

```{r}
setwd("/Volumes/extender/all_data/")

linkage_sk_w1 <- read_csv("/Users/dlf545/Documents/interact_test_data/saskatoon/wave_01/linkage.csv", n_max = 6)

write_csv(linkage_sk_w1, "/Users/dlf545/Documents/interact_test_data/saskatoon/wave_01/linkage_wave_01_saskatoon.csv")

linkage_wave_01_saskatoon <- linkage_sk_w1$interact_id

ethica_wave_01_saskatoon <- linkage_sk_w1$ethica_id
```

## Creating folders

```{}
base_path <- "/Users/dlf545/Documents/interact_test_data/saskatoon/wave_01/sensedoc"

for (name in linkage_wave_01_saskatoon) {

 path <- paste0(base_path, "/", name)
 dir.create(path)

}
```

## Ethica Prep

Creating folders for each participant that exists in the linkage file

```{}
base_path <- "/Users/dlf545/Documents/interact_test_data/saskatoon/wave_01/ethica"

for (name in linkage_wave_01_saskatoon) {

 path <- paste0(base_path, "/", name)
 dir.create(path)

}
```

Reading in a writing ethica data to specific participant folders

```{r}
### Testing with battery data
read_csv(archive_read("/Volumes/extender/all_data/all_studies_battery.tar.gz", file = "1318_battery.csv")) %>%
            filter(., user_id == ethica_wave_01_saskatoon) %>%
            group_split(user_id) %>%
            iwalk(~ write_csv(.x, str_c('battery_wave_01', .y, '_ethica.csv')))
```

```{r}
### GPS Data
read_csv(archive_read("/Volumes/extender/all_data/all_studies_gps.tar.gz", file = "1318_gps.csv")) %>%
            filter(., user_id == ethica_wave_01_saskatoon) %>%
            group_split(user_id) %>%
            iwalk(~ write_csv(.x, str_c('gps_wave_01', .y, '_ethica.csv')))
gc()
```

```{r}
### Bluetooth Data
read_csv(archive_read("/Volumes/extender/all_data/all_studies_bluetooth.tar.gz", file = "1318_bluetooth.csv")) %>%
            filter(., user_id == ethica_wave_01_saskatoon) %>%
            group_split(user_id) %>%
            iwalk(~ write_csv(.x, str_c('bluetooth_wave_01', .y, '_ethica.csv')))
gc()
```

No Bluetooth data

```{r}
### Mbar Data
read_csv(archive_read("/Volumes/extender/all_data/all_studies_mbar.tar.gz", file = "1318_mb_activity_rec.csv")) %>%
            filter(., user_id == ethica_wave_01_saskatoon) %>%
            group_split(user_id) %>%
            iwalk(~ write_csv(.x, str_c('mbar_wave_01', .y, '_ethica.csv')))
gc()
```

```{r}
### Pedometer Data
read_csv(archive_read("/Volumes/extender/all_data/all_studies_pedometer.tar.gz", file = "1318_pedometer.csv")) %>%
            filter(., user_id == ethica_wave_01_saskatoon) %>%
            group_split(user_id) %>%
            iwalk(~ write_csv(.x, str_c('pedometer_wave_01', .y, '_ethica.csv')))
gc()
```

```{r}
### Pedometer Data
read_csv(archive_read("/Volumes/extender/all_data/all_studies_wifi.tar.gz", file = "1318_wifi.csv")) %>%
            filter(., user_id == ethica_wave_01_saskatoon) %>%
            group_split(user_id) %>%
            iwalk(~ write_csv(.x, str_c('wifi_wave_01', .y, '_ethica.csv')))
gc()
```

## Accel Data

Previous code is too slow with GPS and uses too much memory. Need to create sql tables and read from those.

```{r}
sqlite_file <- "ethica_wave_01_saskatoon"
table_name <- "accel_e_wave_01_saskatoon"

inborutils::csv_to_sqlite(csv_file = "/Volumes/extender/all_data/1318_accelerometer.csv", 
              sqlite_file, table_name, pre_process_size = 1000, 
              chunk_size = 50000, show_progress_bar = TRUE)

con <- DBI::dbConnect(SQLite(), dbname = "ethica_wave_01_saskatoon")
accel_w1_ethica_sk <- tbl(con, "accel_e_wave_01_saskatoon")
accel_w1_ethica_sk

### Participant 6407

accel_wave_01_ethica_6407 <- accel_w1_ethica_sk %>% 
                                      filter(user_id == 6407) 
accel_wave_01_ethica_6407 <- accel_wave_01_ethica_6407 %>% collect()

write_csv(accel_wave_01_ethica_6407, "accel_wave_01_ethica_6407.csv")
rm(accel_wave_01_ethica_6407)

### Participant 6396

accel_wave_01_ethica_6396 <- accel_w1_ethica_sk %>% 
                                      filter(user_id == 6396) 
accel_wave_01_ethica_6396 <- accel_wave_01_ethica_6396 %>% collect()

write_csv(accel_wave_01_ethica_6396, "accel_wave_01_ethica_6396.csv")
rm(accel_wave_01_ethica_6396)

### Participant 6403

accel_wave_01_ethica_6403 <- accel_w1_ethica_sk %>% 
                                      filter(user_id == 6403) 
accel_wave_01_ethica_6403 <- accel_wave_01_ethica_6403 %>% collect()

write_csv(accel_wave_01_ethica_6403, "accel_wave_01_ethica_6403.csv")
rm(accel_wave_01_ethica_6403)

```